\section{Results Discussions}
For what concerns the detection part, we can immediately observe that, some images have bounding boxes well detected, others instead not or they do not have any detections at all. 
The main reason why there are those problems are :
\begin{itemize}
    \item Some of the images contains hands with different point of view and, by using a window with static size for all the images (different size for images from 01 to 20 and from 21 to 30) there are multiple detections for the same hand because it is too big compared to the window size. (This can be seen in images like 17,18.19,20 etc.)
    \item Moreover, other images have no detection at all, and this may be cause by the fact that some of the hands have very strong illumination like images 21 and 30.
\end{itemize}
Therefore, even if the result is not 100\% accurate, still it's quite good, because there are only 14 values of the IOU out of 68 that have value equal to 0. So, we can say that the main issue of this solution is the time taken for processing a single image which is very high.\\\\
For what concerns instead the segmentation part, we can observe that, most of the hands are segmented quite well, in fact, all the values of pixel accuracy are above 0.95. However, some different hands have been interpreted (colored) as a single one. (For example in image 01, 02, 14, 15, 18 etc.). This is due to the fact that, when two hands are overlapping one to another the mask produced by the model is connected instead of being separated.

\section{Future Works}
To solve the problems of the detection solution proposed, we can adopt more sophisticated techniques like ad-hoc Neural Networks that are able to recognize objects, by fine-tuning them, in order to recognize only hands (i.e. Yolo, Fast-RCNN, Faster-RCNN, SSD).\\\\
To solve the problem of the segmentation solution proposed, we can proceed by applying an erosion operation on the mask, however if we do so, we need to apply a very strong erosion, with the problem of reducing drastically the size of the mask and therefore the pixel accuracy value will become noticeably small compared to the ones used now. Another way to solve this problem is to use again, ad-hoc / state of the art segmentation methods that, instead of producing the masks as output they will produce the polygons which identify different objects, which, in this case are hands.